First paper - Draft

### 2017-06-02 paper/paper.Rnw
Sample size was too low with current specs - changed to have bigger sample

    df_lower <- filter(df, new_hisced == 1)
    df_upper <- filter(df, new_hisced == 7)

    quan_lower <- try(Hmisc::wtd.quantile(df_lower$escs_trend,
                                          weights = df_lower[[weights]],
                                          probs = c(0.30)))

@@

left_join(sample_size, high_low_sample) %>%
  left_join(ses_sample)

>>>>

    df_lower <- filter(df, new_hisced %in% c(1, 2))
    df_upper <- filter(df, new_hisced == 7)

    quan_lower <- try(Hmisc::wtd.quantile(df_lower$escs_trend,
                                          weights = df_lower[[weights]],
                                          probs = c(0.50)))

@@

m <- left_join(sample_size, high_low_sample) %>%
  left_join(ses_sample) %>%
  arrange(country, year)
